Verifying Demonstrations

### 2018-11-20 paper/DB-anon-cred.tex
Rotates too wide figure

    \(\forall i\in\bin\colon s_i\gets \rho - c_i\alpha \mod q\)
    &
    & \(b\rgets \bin\)
    \\

    \(\forall i\in\bin\colon s_i^{(0)} \rgets \ZZ_q, s_i^{(1)} \gets s_i - 
      s_i^{(0)} \mod q\)
    &
    & Prepare \(B\in \bin^{2|q|+l}\), with \(2|q|\) bits set to \(b\).
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < 2|q| 
        + l, j\gets 0\)} \\

@@

    \(r_i\gets (s_{b_i}^{(0)}\concat s_{b_i}^{(1)})[jb_i + (i-j)(1-b_i)]\)
    & \(\ProtoSendRight{r_i}\)
    & Record \(\Delta t_i\)
    \\

@@

    % null
    &
    & Construct \(s_b^{(0)}\concat s_b^{(1)}\) as the concatenation of \(r_i\)'s for which \(b_i = b\).
    Compute \(s_b\gets s_b^{(0)} + s_b^{(1)}\).
      Accept if \(R = g^{s_b} A^{c_b}\).
    \\

@@

During one round, the prover commits to a random nonce: more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
This is also different from the original Brands-Chaum protocol, in which the prover and verifier jointly construct \emph{one} challenge with \emph{one} response.)

Now the prover randomly chooses \(s_0^{(0)}, s_1^{(0)}\in \ZZ_q\) and computes \(s_0^{(1)} \gets s_0 - s_0^{(0)}, s_1^{(1)} \gets s_1 - s_1^{(0)}\).
\Ie \(s_b\) can be reconstructed by adding the two shares \(s_b^{(0)}, s_b^{(1)}\).

We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
The verifier will request all \(2|q|\) response-bits from one challenge (say \(s_b^{(0)}\concat s_b^{(1)}\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}^{(0)}\concat s_{1-b}^{(1)}\)).
Then the verifier can compute \(s_b = s_b^{(0)} + s_b^{(1)}\) and finally authenticate the prover by checking if \(R = g^{s_b}A^{c_b}\).

@@

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
The verifier will send \(|q| + l < 2|q|\) challenges.
By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but none of the other --- only \(l\leq |q|\) bits of \emph{one of two} information theoretically independent \(|q|\)-bit shares.
Now, the adversary has two options.
First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
However, at this point the adversary must wait for the challenge bit \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
The alternative is to guess \(b\) and extract \(s_b\) for this challenge from the prover.
Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
The adversary can also guess the remaining \(2|q|-l\) bits, which we will discuss in more details below.
The probability of guessing these bits successfully is \(2^{-(2|q|-l)}\).
However, \(l < |q| \implies 2|q|-l > |q|\) and this might thus be more expensive than guessing \(s_{1-b}\) directly, which is \(2^{-|q|}\).
Thus the success probability of the \ac{DBMF} adversary is \emph{at most} \(2^{-n}+2^{-|q|n}\).

@@

The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.

@@

We wanted to formally verify the protocol security properties. 
To realize this, we used the Tamarin prover ~\cite{meier2013tamarin}. 
Tamarin does not include originally the possibility to reason on time and space in its model.
However, thanks to a recent work by Mauw and co-authors~\cite{TamarinDB}, all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.

>>>>

    \(s_0\gets \rho - c_0\alpha \pmod q\)
    &
    & \(b\rgets \bin\)
    \\

    \(s_1\gets \rho - c_1\alpha \pmod q\)
    &
    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\).
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
        l, j\gets 0\)} \\

@@

    \(r_i\gets s_{b_i}[jb_i + (i-j)(1-b_i)]\)
    & \(\ProtoSendRight{r_i}\)
    & Record \(\Delta t_i\)
    \\

@@

    % null
    &
    & Construct \(s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
      b\).
      Accept if \(R = g^{s_b} A^{c_b}\).
    \\

@@

During one round, the prover commits to a random nonce: more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
This is also different from the original Brands-Chaum protocol, in which the 
prover and verifier jointly construct \emph{one} challenge with \emph{one} 
response.

We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
The verifier will request all \(|q|\) response-bits from one challenge (say 
\(s_b\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}\)).
Then the verifier can authenticate the prover by checking if \(R = 
  g^{s_b}A^{c_b}\).

@@

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
The verifier will send \(|q| + l < 2|q|\) challenges.
By replying, the prover reveals \(|q|+l\) bits distributed over \(s_0, 
  s_1\).
\emph{We assume} that learning \(\ceil{(|q|+l)/2}\) bits of \(s_0\) and 
\(\floor{(|q|+l)/2}\) bits of \(s_1\) yields no advantage for the adversary.
Now, the adversary has two options.
First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
However, at this point the adversary must wait for the challenge bit \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
The alternative is to guess \(b\) and extract \(s_b\) for this challenge from the prover.
Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
If the adversary requests \(s_b\) in full, the adversary can also guess the 
remaining \(|q|-l\) bits of \(s_{1-b}\).
Based on our assumption above, the probability of guessing these bits 
successfully is \(2^{-(|q|-l)}\).
Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
\(2^{-n}+2^{-(|q|-l)n}\).

@@

The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.
Thus the probability of success is equivalent of a collision for the responses 
for the chosen challenge --- in each round.

@@

We wanted to formally verify the protocol security properties. To realize this, 
we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
originally the possibility to reason on time and space in its model.
However, thanks to a recent work by Mauw and co-authors~\cite{TamarinDB}, all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.

### 2018-11-20 paper/analysis-performance.tex

\subsection{Distance-bounding anonymous credentials}
The distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available on the market can already enable proofs of proximity for any range of up to 200 meters.
One of the short-term objectives is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
More precisely, they have proposed three different implementations of the Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic implementation running a the application layer to an advanced one running in RFID-emulation mode. 
The results obtained already show that a relay attack can be detected if the adversary introduces a delay of more than 1.5 ms when performing such an attack (most of the existing attacks introduce delays of at least tens of milliseconds).

With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated. 
The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
%Seb: to do add the reference to the following paper at the end of the sentence:
%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$). 
However, this can be reduced to four random number generations and one exponentiation using precomputation.

>>>>

%\subsection{Distance-bounding anonymous credentials}
%The distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available on the market can already enable proofs of proximity for any range of up to 200 meters.
%One of the short-term objectives is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
%For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
%More precisely, they have proposed three different implementations of the Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic implementation running a the application layer to an advanced one running in RFID-emulation mode. 
%The results obtained already show that a relay attack can be detected if the adversary introduces a delay of more than 1.5 ms when performing such an attack (most of the existing attacks introduce delays of at least tens of milliseconds).
%
%With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated. 
%The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
%This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
%%Seb: to do add the reference to the following paper at the end of the sentence:
%%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
%%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
%Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$). 
%However, this can be reduced to four random number generations and one exponentiation using precomputation.
